Drivers of tree regeneration remain challenging to be captured by models of

### 2022-12-06 manuscript/manuscriptRW.Rmd
add co-author in alphabetical order

---
title: Drivers of tree regeneration remain challenging to be captured by models of
  forest dynamics
author:
- Olalla Díaz-Yáñez,
- Yannek Käber,
- Mats Mahnken,
- Samuel Fischer,
- Xavier Morin,
- Manfred Lexer,
- Christian Hochauer,
- Katarina Merganicova,
- Tobias Mette,
- Werner Rammer,
- Kristin H. Braziunas,
- Paola Mairota,
- Josef Bruna,
- Heike Lischke,
- Daniel Scherrer,
- Simon Scheiter,
- Thomas Hickler,
- Tim Anders,
- Jessica Hetzer,
- Harald Bugmann
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    keep_tex: yes
    number_sections: yes
    toc: no
  word_document:
    reference_docx: template_paper.docx
mainfont: Arial
fontsize: 12pt
linestretch: 1.5
bibliography: Regeneration.bib
link-citations: yes
linkcolor: blue
csl: draft.csl
editor_options:
  markdown:
    wrap: 72
header-includes:
- \usepackage[left]{lineno}
- \linenumbers
---

@@

Given the current strategies that are used in models of forest dynamics
to represent tree recruitment, model behavior is facing several problems
and that can have strong impacts on forest dynamic, such as very high
levels of recruitment, which then necessitate excess mortality to early
stages to arrive at correct stand structure and composition. Also, often
inadequately high species diversity in regeneration is simulated. This
is characteristic of \'classical\' forest gap models [@gutiérrez2016],
at least as long as the simulations comprise a multitude of species.
Other models use calibration against local canopy-level data to define
appropriate recruitment levels, which is likely to strongly hamper the
general applicability of these models e.g. under scenarios of climate
change.

@@

Two models, ForClim and ForCEEPs used two alternative model versions.
ForClim variant 1 [@bugmann1996] is based on an establishment module
that adheres closely to the concept introduced by @botkin1972, whereas
ForClim variant 11 is adopting a rather different approach for
establishment model that considers
space filling along with different \'points of entry\' for the action of
specific
environmental factors @huber2020. These two model variants allow us to
evaluate a more process-based establishment module (variant 11) against
a simpler module (variant 1) while the rest of the model structure
remains the same. Similarly,
the two ForCEEPS variants used here allow us to isolate the importance
of the
canopy feedback via seed trees for the quantity and quality of simulated
regeneration, as one variants includes this feedback whereas the other
one does
not.

@@

The simulations were run in the absence of natural disturbances, only
the model LPJ-GUESS had to include HERE LPJ-GUESS PROVIDE [ONE
SENTENCE]{.underline} OF WHY YOU INCLUDED DISTURBANCES AND WHAT TYPE.
The simulations were set up to sample species-specific regeneration
rates per decade and per ha in the equilibrium state of the model,
typically entailing a \"spin-up\" run (as we did not provide any forest
data). The modeling teams decided on the simulated area and how they
derived these samples. The exact length of the simulation was also
decided by the modeling teams (Table \@ref(tab:tableModels)). Further
details on how each modeling team prepared the simulations and the
outputs are available in the SM 2.

@@

On the one hand, the fact that some models feature lower mortality than
expected by Reineke\'s self-thinning rule may point to facilitation, or
simply a higher mortality rate
before the trees had reached 7 cm diameter. On the other hand, the case
of models
such as xComp, PICUS and TreeMig, which are well above the self-thinning
line, may
indicate that they feature higher recruitment mortality in mixed-species
forests
compared to even-aged, single-species forests. However, some models
yielded a mortality rate of recruitment that is broadly compatible with
the self-thinning rule, i.e. 4C and LandClim.

@@

Accurate simulation of tree recruitment rates is pivotal for projecting
the dynamics of forest stand structure and composition. Most of the
models of forest dynamics evaluated here tended to overestimate tree
recruitment rates across the 200 sites. Overestimating has far-reaching
implications regarding biomass (and carbon) turnover, with a potential
overestimation in their capacity for carbon capture [@pugh2019].
Importantly, excess recruitment requires higher mortality rates in later
stages, either -- as observed for
some models -- between the 7 and 10 cm diameter thresholds, or either
before or
shortly after this stage. Correcting for the expected forest densities
at early
stages is thus equivalent to compensating for a first error (excess
recruitment) by committing a second error (excess mortality). Thus, many
models appear to get the right \'answer\', i.e., correct stand structure
and composition, for the wrong reasons. This is problematic particularly
if the models are to be used under novel conditions (e.g., climate
change; @huber2021) or in a decision support context (e.g.,
@thrippleton2021).

In spite of this criticism, it remains remarkable that most of the
models were not overly off
with respect to simulated regeneration levels -- after all, few if any
of the models\' establishment routines are sufficiently constrained by
data, and the resulting degrees of freedom that are available for
modeling regeneration (cf. @konig_tree_2022) could have implied that
model performance would be much worse.

@@

A concluding (\"more positive\") final paragraph.

>>>>

---
title: Drivers of tree regeneration remain challenging to be captured by models of
  forest dynamics
author:
- Olalla Díaz-Yáñez,
- Yannek Käber,
- Tim Anders,
- Kristin H. Braziunas,
- Josef	Bruna,
- Samuel Fischer,
- Jessica Hetzer,
- Thomas Hickler,
- Christian	Hochauer,
- Manfred Lexer,
- Heike	Lischke,
- Mats Mahnken,
- Paola	Mairota,
- Katarina Merganicova,
- Tobias Mette,
- Xavier Morin,
- Werner Rammer,
- Simon	Scheiter,
- Daniel Scherrer,
- Harald Bugmann
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    keep_tex: yes
    number_sections: yes
    toc: no
  word_document:
    reference_docx: template_paper.docx
mainfont: Arial
fontsize: 12pt
linestretch: 1.5
bibliography: Regeneration.bib
link-citations: yes
linkcolor: blue
csl: draft.csl
editor_options:
  markdown:
    wrap: 72
header-includes:
- \usepackage[left]{lineno}
- \linenumbers
---

@@

Given the current strategies that are used in models of forest dynamics
to represent tree recruitment, model behavior is facing several problems
and that can have strong impacts on forest dynamic, such as very high
levels of recruitment, which then necessitate excess mortality to early
stages to arrive at correct stand structure and composition. Also, often
inadequately high species diversity in regeneration is simulated. This
is characteristic of 'classical' forest gap models [@gutiérrez2016], at
least as long as the simulations comprise a multitude of species. Other
models use calibration against local canopy-level data to define
appropriate recruitment levels, which is likely to strongly hamper the
general applicability of these models e.g. under scenarios of climate
change.

@@

Two models, ForClim and ForCEEPs used two alternative model versions.
ForClim variant 1 [@bugmann1996] is based on an establishment module
that adheres closely to the concept introduced by @botkin1972, whereas
ForClim variant 11 is adopting a rather different approach for
establishment model that considers space filling along with different
'points of entry' for the action of specific environmental factors
@huber2020. These two model variants allow us to evaluate a more
process-based establishment module (variant 11) against a simpler module
(variant 1) while the rest of the model structure remains the same.
Similarly, the two ForCEEPS variants used here allow us to isolate the
importance of the canopy feedback via seed trees for the quantity and
quality of simulated regeneration, as one variants includes this
feedback whereas the other one does not.

@@

The simulations were run in the absence of natural disturbances, only
the model LPJ-GUESS had to include HERE LPJ-GUESS PROVIDE [ONE
SENTENCE]{.underline} OF WHY YOU INCLUDED DISTURBANCES AND WHAT TYPE.
The simulations were set up to sample species-specific regeneration
rates per decade and per ha in the equilibrium state of the model,
typically entailing a "spin-up" run (as we did not provide any forest
data). The modeling teams decided on the simulated area and how they
derived these samples. The exact length of the simulation was also
decided by the modeling teams (Table \@ref(tab:tableModels)). Further
details on how each modeling team prepared the simulations and the
outputs are available in the SM 2.

@@

On the one hand, the fact that some models feature lower mortality than
expected by Reineke's self-thinning rule may point to facilitation, or
simply a higher mortality rate before the trees had reached 7 cm
diameter. On the other hand, the case of models such as xComp, PICUS and
TreeMig, which are well above the self-thinning line, may indicate that
they feature higher recruitment mortality in mixed-species forests
compared to even-aged, single-species forests. However, some models
yielded a mortality rate of recruitment that is broadly compatible with
the self-thinning rule, i.e. 4C and LandClim.

@@

Accurate simulation of tree recruitment rates is pivotal for projecting
the dynamics of forest stand structure and composition. Most of the
models of forest dynamics evaluated here tended to overestimate tree
recruitment rates across the 200 sites. Overestimating has far-reaching
implications regarding biomass (and carbon) turnover, with a potential
overestimation in their capacity for carbon capture [@pugh2019].
Importantly, excess recruitment requires higher mortality rates in later
stages, either -- as observed for some models -- between the 7 and 10 cm
diameter thresholds, or either before or shortly after this stage.
Correcting for the expected forest densities at early stages is thus
equivalent to compensating for a first error (excess recruitment) by
committing a second error (excess mortality). Thus, many models appear
to get the right 'answer', i.e., correct stand structure and
composition, for the wrong reasons. This is problematic particularly if
the models are to be used under novel conditions (e.g., climate change;
@huber2021) or in a decision support context (e.g., @thrippleton2021).

In spite of this criticism, it remains remarkable that most of the
models were not overly off with respect to simulated regeneration levels
-- after all, few if any of the models' establishment routines are
sufficiently constrained by data, and the resulting degrees of freedom
that are available for modeling regeneration (cf. @konig_tree_2022)
could have implied that model performance would be much worse.

@@

A concluding ("more positive") final paragraph.
